Appendix

### 2015-05-04 Rmarkdown/appendix.Rmd
Fix formatting
Edits to concluding remarks and appendix
Correct a typo in appendix
Correct Python version

\begin{equation*}
\label{eq:transition_matrix_nid}
\Pi =
 \begin{pmatrix}
  (1 - p_{h'}) + c p_{h} & p_{h'} - c p_{h} \\
  \big [ (1 - p_{h'}) + c p_{h} \big ] (1 - p_{h}) & \big [ p_{h'} + c (1 - p_{h}) \big ] p_{h}
 \end{pmatrix}
\end{equation*}

@@

__TODO: What is the general restriction on $c$ when $p_{h, i} \neq p_{h', i'}$?__

\subsection{Estimate of number of CpGs used by \citet{Lacey:2013iy}}\label{app:lacey}

@@

The analyses described in my thesis made extensive use of R (`R Under development (unstable) (2014-10-29 r66891)` and `R version 3.2.0 (2015-04-16)`) and Python (`v2.6.6`). All analyses were run on one of the servers described above. The scripts used to prepare the results for each chapter are available from \url{https://github.com/PeteHaitch/phd_thesis_analyses}. Further details of software used are available in Appendix \ref{app:software_details}.

>>>>

\begin{equation*}
\label{eq:transition_matrix_nid}
\Pi =
 \begin{pmatrix}
  (1 - p_{h'}) +c p_{h} & p_{h'} -c p_{h} \\
  (1 - p_{h'}) -c (1 - p_{h}) & p_{h'} + c (1 - p_{h})
 \end{pmatrix}
\end{equation*}

@@

\subsection{Estimating the number of CpGs used by \citet{Lacey:2013iy}}\label{app:lacey}

@@

The analyses described in my thesis made extensive use of R (`R Under development (unstable) (2014-10-29 r66891)` and `R version 3.2.0 (2015-04-16)`) and Python (`v2.7`). All analyses were run on one of the servers described above. The scripts used to prepare the results for each chapter are available from \url{https://github.com/PeteHaitch/phd_thesis_analyses}. Further details of software used are available in Appendix \ref{app:software_details}.
